Meta-analysis

### 2020-07-23 04_MetaAnalysis.Rmd
amend T-crit value in 03_prep_data.rmd and re-Knit all subsequently effected files

In this result we can see that the `Early` treatment is not significantly different to the intercept, which in this case is the mean of the no spray `control`.
However the other treatments are significantly different from the no-spray control (intercept).
The $Q_M$ [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, shows the moderators significantly influence the model ($Q_M =$ `r PM_mv$QM` $, df = $ `r PM_mv$m`, `r reportP(PM_mv$QMp)`) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = $`r PM_mv$QM` $, df = $`r PM_mv$k - PM_mv$m`, `r reportP(PM_mv$QEp)` ) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.

@@

```{r profile_plots, message=FALSE, results="hide"}
profile(PM_mv, tau2 = 1)
profile(PM_mv, tau2 = 2)
profile(PM_mv, tau2 = 3)
profile(PM_mv, tau2 = 4)
profile(PM_mv, tau2 = 5)
```

>>>>

In this result we can see that the `Early` treatment is not significantly different to the intercept, which in this case is the mean of the no spray `control`.
However the other treatments are significantly different from the no-spray control (intercept).
The $Q_M$ [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, shows the moderators significantly influence the model ($Q_M =$ `r PM_mv$QM` $,df =$ `r PM_mv$m`, `r reportP(PM_mv$QMp)`) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
The analysis shows there is still a significant amount of residual heterogeneity ($Q_E =$ `r PM_mv$QM` $,df=$ `r PM_mv$k - PM_mv$m`, `r reportP(PM_mv$QEp)` ) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.

@@

```{r profile_plots, eval=FALSE, message=FALSE, include=FALSE, results="hide"}
profile(PM_mv, tau2 = 1)
profile(PM_mv, tau2 = 2)
profile(PM_mv, tau2 = 3)
profile(PM_mv, tau2 = 4)
profile(PM_mv, tau2 = 5)
```
